A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 textos/dsrt/engaoi.tex
eng

Ns-2 simulator \cite{mccanne:nsn} was used to simulate and compare the interest management algorithms described in this paper. This simulator allows the user to create code of the specific application which will be simulated. In our case, it was simulated a server which should send state updates to the client responsible for one of the avatars in the region managed by that server. Based on the location of the other avatars and on the chosen interest management algorithm, the server decided which other avatars had a relevant state to the client in question. Through the simulations, it was obtained the necessary upload bandwidth for one client. It was not considered necessary to simulate every client connected to the server simultaneously because every one of them had the same behavior. To find the total upload bandwidth usage, we just multiply the value found in the simulation by the number of clients connected to that server. Another question is that the upload bandwidth usage by the server is much higher than download. If it receives $n$ actions, each from one of the $n$ clients, it must send, in the worst case, $O(n^2)$ state updates, because every player needs the state of the others. Therefore, it was only necessary to measure the upload traffic from the server.

Outra questão é que o consumo de largura de banda de envio do servidor é muito maior que o de recepção - se ele recebe $n$ ações, cada uma oriunda de um dos $n$ clientes, é necessário, no pior caso, enviar $O(n^2)$ atualizações de estado, pois cada jogador precisaria do estado de todos os outros. Assim sendo, foi necessário apenas medir a banda de transmissão utilizada.

%falar do svoboda e do kim??...
Em trabalhos como \cite{yu2007nas}, \cite{kim2005tcm} e \cite{svoboda2007taa}, é analisado o tráfego de rede gerado por jogos em larga escala. Baseado nestes trabalhos, e adotando uma postura conservadora, foram decididos os seguinte parâmetros para serem utilizados na simulação:

\begin{itemize}
 \item Intervalo normal de atualização: 250 ms;
 \item Tamanho do pacote de atualização de estado de uma única entidade: 100 bytes;
 \item Duração de cada sessão de jogo simulada: 20 min;
 \item Área do ambiente virtual: 750 x 750;
 \item Alcance da visão: 120;
 \item Distância crítica: 40;
 \item Ângulo de visão: 180°.
\end{itemize}

>>>>

Ns-2 simulator \cite{mccanne:nsn} was used to simulate and compare the interest management algorithms described in this paper. This simulator allows the user to create code of the specific application which will be simulated. In our case, it was simulated a server which should send state updates to the client responsible for one of the avatars in the region managed by that server. Based on the location of the other avatars and on the chosen interest management algorithm, the server decided which other avatars had a relevant state to the client in question.

Through the simulations, it was obtained the server upload bandwidth usage with one client. It was not considered necessary to simulate every client connected to the server simultaneously because every one of them had the same behavior. To find the total upload bandwidth usage, we just multiply the value found in the simulation by the number of clients connected to that server. Another question is that the upload bandwidth usage by the server is much higher than download. If it receives $n$ actions, each from one of the $n$ clients connected to it, it must send, in the worst case, $O(n^2)$ state updates, because each player needs the state of the others. Therefore, it was only necessary to measure the upload traffic from the server.

%falar do svoboda e do kim??...

Some works, as \cite{yu2007nas}, \cite{kim2005tcm} and \cite{svoboda2007taa}, analyse the network traffic generated by large scale games. Based on these analysis, and adopting a conservative posture, the following parameters have been decided to be used in the simulations:

\begin{itemize}
 \item Normal update interval: 250 ms;
 \item State update packet size for one entity: 100 bytes;
 \item Duration of each simulated game session: 20 min;
 \item Virtual environment area: 750 x 750;
 \item View distance: 120;
 \item Critical distance: 40;
 \item View angle: 180°.
\end{itemize}
